IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks

### 2016-07-05 ms_infocus.tex
Minor edits.
Minor edits, references.
Added refs and Intro text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS: In Focus comment paper for Journal of Animal Ecology.
%% Draft
%% April 2016
%% Revised version: 
%% Original version wordcount: 8165 words.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
\usepackage{comment}
\usepackage{jae}
\title{IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks}
\running{Forbidden interactions}

@@

\nwords{0000}
\ntables{0}
\nfig{1}
\nref{00}

@@

  \textbf{Species-specific traits and life-history characteristics constrain the ways organisms interact in nature. For example, gape-limited predators are constrained in the sizes of prey they can handle and efficiently consume. When we consider the ubiquity of such constrains it is evident how hard it can be to be a generalist partner in ecological interactions: a free living animal or plant can't simply interact with every available partner it encounters. Some pairwise interactions among coexisting species simply do not occur; they are impossible to observe despite the fact that partners coexist in the same place. Sazatornil et al. explore the nature of such constraints in the mutualisms among hawkmoths and the plants they pollinate. In this iconic interacion, used by Darwin and Wallace to vividly illustrate the power of natural selection in shaping evolutionary change, both pollinators and plants are sharply constrained in their interaction modes and outcomes. } \\
%\end{abstract}

@@

%---------------------------------------------------------------------------------
Size-limited foragers show clear restrictions on the size of prey items they can efficiently handle. In the case of plant-pollinator interactions, size uncoupling between pollinator bodies and flower sizes or structure are specially relevant in filtering out a range of potential partners \citep{Cocucci:2009}. The idea, when applied to the bizarre flowers of some plants pollinated by sphingid moths (Lepidoptera: Sphingidae), was seminal in Darwinian evolutionary theory to support the potential of natural selection in shaping adaptations. Wallace \citep{Wallace:1867} in his book, \textit{Creation by law}, vividly uses the famous example of the Malagasy orchid and its sphingid pollinator to refute the arguments of the Duke of Argyll against natural selection and Darwinism:

@@

Recent work by Sazatornil \textit{et al.} \citep{Sazatornil:2016} provides evidences that the types of trait mismatching outlined in Fig. 1 limit the ranges of host plants for sphingid pollinators, and ultimately shape their complex plant-pollinator networks.

@@

@@

\bibitem{More:2012}
Moré, M., Amorim, F.W., Benitez-Vieyra, S., Medina, A.M., Sazima, M. \& Cocucci, A.A. (2012) Armament Imbalances: Match and Mismatch in Plant-Pollinator Traits of Highly Specialized Long-Spurred Orchids (ed M Heil). PLoS ONE, 7, e41878.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MS: In Focus comment paper for Journal of Animal Ecology.
%% Draft
%% April 2016
%% Revised version: 
%% Original version wordcount: 910 words.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt]{article}
\usepackage{comment}
\usepackage{jae}
\title{IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks}
\running{Forbidden interactions}

@@

\nwords{910}
\ntables{0}
\nfig{1}
\nref{7}

@@

  \textbf{Species-specific traits and life-history characteristics constrain the ways organisms interact in nature. For example, gape-limited predators are constrained in the sizes of prey they can handle and efficiently consume. When we consider the ubiquity of such constrains it is evident how hard it can be to be a generalist partner in ecological interactions: a free living animal or plant can't simply interact with every available partner it encounters. Some pairwise interactions among coexisting species simply do not occur; they are impossible to observe despite the fact that partners coexist in the same place. Sazatornil \textit{et al.} \citep{Sazatornil:2016} explore the nature of such constraints in the mutualisms among hawkmoths and the plants they pollinate. In this iconic interacion, used by Darwin and Wallace to vividly illustrate the power of natural selection in shaping evolutionary change, both pollinators and plants are sharply constrained in their interaction modes and outcomes. } \\
%\end{abstract}

@@

%---------------------------------------------------------------------------------
Size-limited foragers show clear restrictions on the size of prey items they can efficiently handle. In the case of plant-pollinator interactions, size uncoupling between pollinator bodies and flower sizes or structure are specially relevant in filtering out a range of potential partners \citep{Cocucci:2009}. The idea, when applied to the bizarre flowers of some plants pollinated by sphingid moths (Lepidoptera: Sphingidae), was seminal in Darwinian evolutionary theory to support the potential of natural selection in shaping adaptations \citep{Arditti:2012}. Wallace \citep{Wallace:1867} in his book, \textit{Creation by law}, vividly uses the famous example of the Malagasy orchid and its sphingid pollinator to refute the arguments of the Duke of Argyll against natural selection and Darwinism:

@@

Recent work by Sazatornil \textit{et al.} \citep{Sazatornil:2016} provides evidences that the types of trait mismatching outlined in Fig. 1 limit the ranges of host plants for sphingid pollinators, and ultimately shape their complex plant-pollinator networks. By using a comparative analysis of five different hawkmoth/flower assemblages across four South American biotas (Atlantic rainforest and Cerrado in Brazil, Chaco, and the Chaco-Yungas transition in Argentina) they tested the contributions of phenotypic matching to explain observed patterns of moth-flower interactions.

Yet Sazatornil \textit{et al.} do not include unobserved interactions in their quantifications of mismatches, so the test of the mismatch hypothesis actually includes also forbidden links effects: a full mismatch of corolla tube/proboscis lengths actually meaning a forbidden link.

@@

\bibitem{Arditti:2012}
Arditti, J., Elliott, J., Kitching, I.J. \& Wasserthal, L.T. (2012) “Good Heavens what insect can suck it”–Charles Darwin, \textit{Angraecum sesquipedale} and \textit{Xanthopan morganii praedicta}. Botanical Journal of the Linnean Society, 169, 403–432.

@@

\bibitem{More:2012}
Moré, M., Amorim, F.W., Benitez-Vieyra, S., Medina, A.M., Sazima, M. \& Cocucci, A.A. (2012) Armament imbalances: match and mismatch in plant-pollinator traits of highly specialized long-spurred orchids (ed M. Heil). PLoS ONE, 7, e41878.
